---
title: "Delaware Scenario Report"
author: "Author: Testing"
output:
  html_document:
    df_print: paged
    fig_caption: true
    theme: cerulean
bibliography: ReportReferences.bib
params:
  continue_on_error: TRUE
  config_file: "config.yml"
  state_usps: "DE"  #state USPS...must provided
  included_state: "DE" #two digit abbreviation of state to produce county-level report
  sim_end_date: "2020-12-31" #date at which all results are truncated
  pdeath_default: "med" # which of config$hospitalization$parameters$p_death_names to display for county-level tables
---

Prepared by [Johns Hopkins ID Dynamics](https://iddynamics.jhsph.edu/) Working Group  
Updated `r Sys.Date()`

**FOR PLANNING PURPOSES ONLY: NOT A FORECAST**

```{r setup, include=F}
## Block with general knitr options, libray load, etc. Nothing specific to the project.
knitr::opts_knit$set(root.dir = "../..") ##Assumes we are in a subdirectory of notebooks
knitr::opts_chunk$set(
    echo = FALSE,
    fig.align = "center",
    message = FALSE,
    warning = FALSE,
    error = params$continue_on_error,
    cache.lazy = FALSE,
    bitmapType = "cairo"
    )
knitr::opts_knit$set(eval.after = 'fig.cap') ##Allows us to set a variable to figure caption in the block

options(scipen=999)

#Preamble
library(tidyverse)
library(covidcommon)
library(report.generation)
library(covidImportation)
library(doParallel)

nfiles <- NA ## set to a number for test reports.
nfiles2 <- ifelse(nfiles <= 50, nfiles, 50) ## for plotting

if (params$state_usps=="[STATE USPS]") {stop("Must define a target state by USPS code.")}
ncores <- detectCores() - 1 ## number of cores to use for loading data

```

```{r  load_config}
reportStateUSPS <- params$state_usps 

## Block loads the config file and geodata
config <- covidcommon:::load_config(params$config_file)
geodata <- load_geodata_file(file.path(config$spatial_setup$base_path, config$spatial_setup$geodata),
                             geoid_len=5)
included_geoids <- (geodata %>% filter(USPS==reportStateUSPS))$geoid

scn_dirs <- paste(config$name,config$interventions$scenarios,sep='_')

```

```{r load_shapefile}
## Load shapefile
shp <- load_shape_file(filename = file.path(config$spatial_setup$base_path, config$spatial_setup$shapefile_name),
                       to_lower = TRUE,
                       geoid_len = 5)
```

```{r  set_region}
## block sets the geoids + names to included in report + alphabetizes across all counties
  included_geoids <- geodata %>% filter(USPS %in% params$included_state) %>% select(geoid) %>% arrange(geoid) %>% unlist()
  included_geoid_names <- shp$name[match(included_geoids, shp$geoid)]
```

```{r config_vals}
nscenarios <- length(config$interventions$scenarios)
sim_start_date <- config$start_date
sim_end_date <- config$end_date
report_loc <- config$report_location_name
modeled_loc <- paste(config$spatial_setup$modeled_states, collapse = ", ")
census_year <- config$spatial_setup$census_year
incub_period <- 1/eval(parse(text=config$seir$parameters$sigma))
infect_period <- c(1/(eval(parse(text=config$seir$parameters$gamma$high))),
                   1/(eval(parse(text=config$seir$parameters$gamma$low))))
R0_range <- c(config$seir$parameters$R0s$low, config$seir$parameters$R0s$high)
modeled_states <- state.name[which(state.abb %in% config$spatial_setup$modeled_states)]
```

We compared `r nscenarios` intervention scenarios for model simulations from `r print_pretty_date(sim_start_date)` through `r print_pretty_date(sim_end_date)`:

1. *Lockdown followed by Worst-Case Uncontrolled Spread:* This scenario has statewide school closures from March 13-19 followed by a statewide stay-at-home policy from March 19 through May 14. All interventions are then removed (back to worst-case uncontrolled transmission) starting May 15.

1. *Lockdown followed by Test and Isolate:* This scenario has statewide school closures from March 13-19 followed by a statewide stay-at-home policy from March 19 through May 14. From May 15 through December 31, there is a targeted test and isolate strategy similar to that implemented in South Korea.

1. *Lockdown followed by Moderate Social Distancing:* This scenario has statewide school closures from March 13-19 followed by a statewide stay-at-home policy from March 19 through May 14. From May 15 through December 31, there is moderately restrictive social distancing similar to that in US cities during the 1918 influenza pandemic.


```{r rmd_formatting}
scen_desc_str <- "three scenarios with 8-week lockdown followed by 1) worst-case uncontrolled spread, 2) targeted testing and isolation, and 3) moderately restrictive social distancing"
fig_counter <- 1
tab_counter <- 1
```

```{r load_hosp_geocombined_totals}

doParallel::registerDoParallel(ncores)

state_hosp_totals <- list()
for (i in 1:length(config$hospitalization$parameters$p_death_names)) {
    state_hosp_totals[[i]] <- load_hosp_geocombined_totals(scn_dirs,
                                               num_files = nfiles,
                                               scenariolabels = config$report$formatting$scenario_labels,
                                               name_filter= config$hospitalization$parameters$p_death_names[i],
                                               incl_geoids = included_geoids,
                                               geoid_len = 5,
                                               file_extension="auto") %>%
        mutate(pdeath=config$hospitalization$parameters$p_death[i])
}

state_hosp_totals <- dplyr::bind_rows(state_hosp_totals)

doParallel::stopImplicitCluster()
registerDoSEQ()
```

```{r hosp_summary_fig, fig.cap = cap}
plot_ts_hosp_state_sample(state_hosp_totals,
                          varname = "NhospCurr",
                          varlabel = "Daily hospital occupancy",
                          num_sims = 25,
                          scenario_labels = config$report$formatting$scenario_labels,
                          scenario_cols = config$report$formatting$scenario_colors,
                          sim_start_date = config$start_date,
                          sim_end_date = config$end_date,
                          pdeath_level = 0.01)

cap <- paste0("**Fig. ", fig_counter, "**: Daily state-level hospital occupancy for 25 simulation realizations for ", scen_desc_str, "at 1 % IFR assumptions.")
fig_counter <- fig_counter + 1
```


```{r load_cum_inf_geounit_dates}
###Load cumulative infections on specific dates
doParallel::registerDoParallel(ncores)

cum_inf_dates <- load_cum_inf_geounit_dates(scn_dirs,
                           num_files = nfiles,
                           display_dates = config$report$formatting$display_dates,
                           scenariolabels = config$report$formatting$scenario_labels,
                           incl_geoids = included_geoids,
                           geoid_len = 5,
                           file_extension="auto")

doParallel::stopImplicitCluster()
registerDoSEQ()
```

```{r load_csse_data}
## load CSSE data 
jhu_dat <- load_jhu_csse_for_report(states = modeled_states, update=FALSE) ## change to update=FALSE after the data is pulled for the first time
```


```{r, child=reference_chunk("planning_models.Rmd")}
```

## State Level Results

### Summary

`r paste0("**Tab.", tab_counter, "**: Summary across", scen_desc_str, ". Estimates are presented across", length(config$report$formatting$display_dates)+1, "time periods for 1% infection fatality ratio (IFR) assumptions.")`

```{r scn_time_sum}
make_scn_time_summary_table_withVent(state_hosp_totals %>% dplyr::filter(pdeath==.01), 
                                    config$report$formatting$display_dates,
                                    pi_low = 0.025,
                                    pi_high = 0.975,
                                    round_digit = -1)
tab_counter <- tab_counter+1
```


### Diversity of Possible Outcomes

```{r  death_histograms, fig.cap = cap, fig.width = 12}
##Chunk plots the distribution of hospitalizations at multiple time points

show_dates <- config$report$formatting$display_dates
hist_plts <- list()

for (i in 1:length(show_dates)) {
    hist_plts[[i]] <- plot_hist_incidHosp_state(state_hosp_totals,
                                           var_name = "NincidHosp",
                                           scenario_labels =  config$report$formatting$scenario_labels,
                                           scenario_cols =  config$report$formatting$scenario_colors,
                                           sim_start_date = config$start_date,
                                           summary_date = show_dates[i],
                                           pdeath_level = 0.01)
}

ggpubr::ggarrange(plotlist=hist_plts, nrow=1)


cap <- paste("**Fig.", fig_counter, "**: Distribution of cumulative hospital admissions for", scen_desc_str, "at 1% IFR assumptions. Each bar represents a bin of 2,000 hospitalizations.")
fig_counter <- fig_counter+1
```

### Boxplots for State Level Results

```{r, BOXPLOTSSTATE}

##Boxplot of peak hospital occupancy
hosp_fig <- boxplot_by_timeperiod(state_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NhospCurr)%>%rename(N=NhospCurr),
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,                        
          period_breaks=config$report$formatting$display_dates,
                            stat="peak")+
  scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Peak Hospital Occupancy")


##Boxplot of peak ICU occupancy
icu_fig <- boxplot_by_timeperiod(state_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NICUCurr)%>%rename(N=NICUCurr),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Peak ICU Occupancy") 

##Boxplot of deaths in period
deaths_period <- boxplot_by_timeperiod(state_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidDeath)%>%rename(N=NincidDeath),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Deaths in Period") 

##Boxplot of infections in period
infections_period <- boxplot_by_timeperiod(state_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidInf)%>%rename(N=NincidInf),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Infections in Period") 

##Boxplot of ICU admissions in period
icu_period <- boxplot_by_timeperiod(state_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidICU)%>%rename(N=NincidICU),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("ICU Admissions in Period") 

##Boxplot of hospital admissions in period
hosp_period <- boxplot_by_timeperiod(state_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidHosp)%>%rename(N=NincidHosp),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Hospital Admissions in Period") 

##Boxplot of incident ventilations in period
vent_period <- boxplot_by_timeperiod(state_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidVent)%>%rename(N=NincidVent),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Incident Ventilations in Period") 

##Boxplot of peak ventilator usage in period
peak_vent <- boxplot_by_timeperiod(state_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NVentCurr)%>%rename(N=NVentCurr),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Peak Ventilator in Use in Period") 

ggpubr::ggarrange(plotlist=list(hosp_fig), nrow=1, legend="bottom",
           common.legend = FALSE)   
ggpubr::ggarrange(plotlist=list(icu_fig), nrow=1, legend="bottom",
           common.legend = FALSE)
ggpubr::ggarrange(plotlist=list(deaths_period), nrow=1, legend="bottom",
           common.legend = FALSE)   
ggpubr::ggarrange(plotlist=list(infections_period), nrow=1, legend="bottom",
           common.legend = FALSE)   
ggpubr::ggarrange(plotlist=list(icu_period), nrow=1, legend="bottom",
           common.legend = FALSE)
ggpubr::ggarrange(plotlist=list(hosp_period), nrow=1, legend="bottom",
           common.legend = FALSE) 
ggpubr::ggarrange(plotlist=list(vent_period), nrow=1, legend="bottom",
           common.legend = FALSE) 
ggpubr::ggarrange(plotlist=list(peak_vent), nrow=1, legend="bottom",
           common.legend = FALSE)                                
```

## Scenario Summaries

```{r load_special_data}

## WE DON'T HAVE BED DATA... HOW TO GET BED DATA??
## source("R/load_beds_by_county_[STATE].R") ## R/load_beds_by_county_early_march.R
## bedtype <- "staffed ICU"
## vname <- "n_icu_bed_staffed"
## hosp_vname <- "icu_curr"
## occup_assum <- 0.68 ## assumes ICU occupancy is 68% per county over time on non-COVID patients
## bedtype_label <- paste("Available", bedtype, "ICU beds, calculated as", (1-occup_assum)*100, "% of", bedtype, "Beds")

## beddata <- load_beds_by_county_md(filename = "data/east-coast/md_hospbeddata.csv", ## "data/DPH/GACH ICU Beds By County Early March.xlsx"
##                                    shapefile = shp,
##                                    varname = vname,
##                                    bed_percentage = 1-occup_assum)


```

```{r load_hosp_geounit_threshold}
## doParallel::registerDoParallel(ncores)

## ## dataframe to show when hosp_curr exceeds bed data by county
## thresholddat <- load_hosp_geounit_threshold(scn_dirs,
##                                             num_files = nfiles,
##                                             threshold = beddata,
##                                             name_filter = "high",
##                                             variable = hosp_vname,
##                                             end_date = config$end_date,
##                                             incl_geoids = included_geoids,
##                                             scenario_labels = config$report$formatting$scenario_labels,
##                                             geoid_len = 5)
## doParallel::stopImplicitCluster()
## registerDoSEQ()
```

### Scenario 1: Lockdown followed by Worst-Case Uncontrolled Spread

1. *Lockdown followed by Worst-Case Uncontrolled Spread:* This scenario has statewide school closures from March 13-19 followed by a statewide stay-at-home policy from March 19 through May 14. All interventions are then removed (back to worst-case uncontrolled transmission) starting May 15.


`r paste("**Tab.", tab_counter, "** State-level summary for", config$report$formatting$scenario_labels[1], "scenario reported for the period from", sim_start_date, "through the dates specified by the column headers.")`

```{r scn_state_table1}
make_scn_state_table(config$report$formatting$scenario_labels[1],
                     state_hosp_totals,
                     table_dates = config$report$formatting$display_dates,
                     pdeath_labels = config$report$formatting$pdeath_labels,
                     pdeath_filecode = config$hospitalization$parameters$p_death)

tab_counter <- tab_counter+1
```


```{r ARmaps1, fig.cap = cap}
ARmap1 <- plot_geounit_attack_rate_map(cum_inf_dates,
                            geodata,
                            shp,
                            scenariolabel = config$report$formatting$scenario_labels[1],
                            display_date = config$report$formatting$display_dates[1],
                            viridis_palette = "plasma",
                            popnodes = config$spatial_setup$popnodes)

ARmap2 <- plot_geounit_attack_rate_map(cum_inf_dates,
                            geodata,
                            shp,
                            scenariolabel = config$report$formatting$scenario_labels[1],
                            display_date = config$report$formatting$display_dates[2],
                            viridis_palette = "viridis",
                            popnodes = config$spatial_setup$popnodes)

ARmap3 <- plot_geounit_attack_rate_map(cum_inf_dates,
                            geodata,
                            shp,
                            scenariolabel = config$report$formatting$scenario_labels[1],
                            display_date = config$report$formatting$display_dates[3],
                            viridis_palette = "cividis")
cowplot::plot_grid(ARmap1, ARmap2, ARmap3, ncol=3)

cap <- paste("**Fig.", fig_counter, "** County-level map of infections per 10,000 for", config$report$formatting$scenario_labels[1], " strategy.")
fig_counter <- fig_counter+1
```

### Scenario 2: Lockdown followed by Test and Isolate

2. *Lockdown followed by Test and Isolate:* This scenario has statewide school closures from March 13-19 followed by a statewide stay-at-home policy from March 19 through May 14. From May 15 through December 31, there is a targeted test and isolate strategy similar to that implemented in South Korea.


`r paste("**Tab.", tab_counter, "** State-level summary for", config$report$formatting$scenario_labels[2], "scenario reported for the period from", sim_start_date, "through the dates specified by the column headers.")`

```{r scn_state_table2}
make_scn_state_table(config$report$formatting$scenario_labels[2],
                     state_hosp_totals,
                     table_dates = config$report$formatting$display_dates,
                     pdeath_labels = config$report$formatting$pdeath_labels,
                     pdeath_filecode = config$hospitalization$parameters$p_death)

tab_counter <- tab_counter+1
```


```{r ARmaps2, fig.cap = cap}
ARmap1 <- plot_geounit_attack_rate_map(cum_inf_dates,
                            geodata,
                            shp,
                            scenariolabel = config$report$formatting$scenario_labels[2],
                            display_date = config$report$formatting$display_dates[1],
                            viridis_palette = "plasma",
                            popnodes = config$spatial_setup$popnodes)

ARmap2 <- plot_geounit_attack_rate_map(cum_inf_dates,
                            geodata,
                            shp,
                            scenariolabel = config$report$formatting$scenario_labels[2],
                            display_date = config$report$formatting$display_dates[2],
                            viridis_palette = "viridis",
                            popnodes = config$spatial_setup$popnodes)

ARmap3 <- plot_geounit_attack_rate_map(cum_inf_dates,
                            geodata,
                            shp,
                            scenariolabel = config$report$formatting$scenario_labels[2],
                            display_date = config$report$formatting$display_dates[3],
                            viridis_palette = "cividis")
cowplot::plot_grid(ARmap1, ARmap2, ARmap3, ncol=3)

cap <- paste("**Fig.", fig_counter, "** County-level map of infections per 10,000 for", config$report$formatting$scenario_labels[2], " strategy.")
fig_counter <- fig_counter+1
```

### Scenario 3: Lockdown followed by Moderate Social Distancing

3. *Lockdown followed by Moderate Social Distancing:* This scenario has statewide school closures from March 13-19 followed by a statewide stay-at-home policy from March 19 through May 14. From May 15 through December 31, there is moderately restrictive social distancing similar to that in US cities during the 1918 influenza pandemic.


`r paste("**Tab.", tab_counter, "** State-level summary for", config$report$formatting$scenario_labels[3], "scenario reported for the period from", sim_start_date, "through the dates specified by the column headers.")`

```{r scn_state_table3}
make_scn_state_table(config$report$formatting$scenario_labels[3],
                     state_hosp_totals,
                     table_dates = config$report$formatting$display_dates,
                     pdeath_labels = config$report$formatting$pdeath_labels,
                     pdeath_filecode = config$hospitalization$parameters$p_death)

tab_counter <- tab_counter+1
```


```{r ARmaps3, fig.cap = cap}
ARmap1 <- plot_geounit_attack_rate_map(cum_inf_dates,
                            geodata,
                            shp,
                            scenariolabel = config$report$formatting$scenario_labels[3],
                            display_date = config$report$formatting$display_dates[1],
                            viridis_palette = "plasma",
                            popnodes = config$spatial_setup$popnodes)

ARmap2 <- plot_geounit_attack_rate_map(cum_inf_dates,
                            geodata,
                            shp,
                            scenariolabel = config$report$formatting$scenario_labels[3],
                            display_date = config$report$formatting$display_dates[2],
                            viridis_palette = "viridis",
                            popnodes = config$spatial_setup$popnodes)

ARmap3 <- plot_geounit_attack_rate_map(cum_inf_dates,
                            geodata,
                            shp,
                            scenariolabel = config$report$formatting$scenario_labels[3],
                            display_date = config$report$formatting$display_dates[3],
                            viridis_palette = "cividis")
cowplot::plot_grid(ARmap1, ARmap2, ARmap3, ncol=3)

cap <- paste("**Fig.", fig_counter, "** County-level map of infections per 10,000 for", config$report$formatting$scenario_labels[3], " strategy.")
fig_counter <- fig_counter+1
```

## County-Specific Results


```{r county-level read, results="asis"}

## CREATES HEADER + SUMMARY TABLE FOR EACH GEOID

  cat("  \n -----------------------------  \n")
  cat("  \n###",  as.character(included_geoid_names[2]), "  \n")

  cat( paste("**Tab.", tab_counter, 
             " **: Summary across", scen_desc_str, " for the county of ", included_geoid_names[2], 
             ". Estimates are presented across", 
             length(config$report$formatting$display_dates)+1, 
             "time periods for 1% IFR assumptions.") )
  
  ## UNCOMMENT TO RUN PARALLEL (ALSO DEREGIASTER AT END)
  doParallel::registerDoParallel(ncores)

  ### Load county level totals
  scn_dirs <- paste(config$name,config$interventions$scenarios,sep='_')

  tmp_hosp_totals <- list()

  tmp_hosp_totals[[1]] <- load_hosp_geocombined_totals(scn_dirs = scn_dirs,
                                                       scenariolabels = config$report$formatting$scenario_labels,
                                                       name_filter = params$pdeath_default,
                                                       incl_geoids = included_geoids[2],
                                                       geoid_len = 5) %>%
        mutate(pdeath=config$hospitalization$parameters$p_death[which(config$hospitalization$parameters$p_death_names == params$pdeath_default)])


  ## UNCOMMENT TO RUN PARALLEL
  doParallel::stopImplicitCluster()

  tmp_hosp_totals <- dplyr::bind_rows(tmp_hosp_totals)
  
  cat( knitr::knit_print(make_scn_time_summary_table_withVent(tmp_hosp_totals, config$report$formatting$display_dates)) )
  
  cat("  \n")
  tab_counter <- tab_counter + 1

```

### Boxplots for County Level Results

```{r, BOXPLOTSCOUNTY}

##Boxplot of peak hospital occupancy
hosp_fig <- boxplot_by_timeperiod(tmp_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NhospCurr)%>%rename(N=NhospCurr),
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,                        
          period_breaks=config$report$formatting$display_dates,
                            stat="peak")+
  scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Peak Hospital Occupancy")


##Boxplot of peak ICU occupancy
icu_fig <- boxplot_by_timeperiod(tmp_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NICUCurr)%>%rename(N=NICUCurr),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Peak ICU Occupancy") 

##Boxplot of deaths in period
deaths_period <- boxplot_by_timeperiod(tmp_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidDeath)%>%rename(N=NincidDeath),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Deaths in Period") 

##Boxplot of infections in period
infections_period <- boxplot_by_timeperiod(tmp_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidInf)%>%rename(N=NincidInf),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Infections in Period") 

##Boxplot of ICU admissions in period
icu_period <- boxplot_by_timeperiod(tmp_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidICU)%>%rename(N=NincidICU),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("ICU Admissions in Period") 

##Boxplot of hospital admissions in period
hosp_period <- boxplot_by_timeperiod(tmp_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidHosp)%>%rename(N=NincidHosp),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Hospital Admissions in Period") 

##Boxplot of incident ventilations in period
vent_period <- boxplot_by_timeperiod(tmp_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NincidVent)%>%rename(N=NincidVent),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Incident Ventilations in Period") 

##Boxplot of peak ventilator usage in period
peak_vent <- boxplot_by_timeperiod(tmp_hosp_totals %>% 
                                    select(time, sim_num, scenario_name,
                                           NVentCurr)%>%rename(N=NVentCurr),
          period_breaks=config$report$formatting$display_dates,
          scenario_labels=config$report$formatting$scenario_labels,
          scenario_colors=config$report$formatting$scenario_colors,
                            stat="peak")+scale_y_sqrt()+
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.title = element_blank())+
  ylab("Peak Ventilator in Use in Period") 

ggpubr::ggarrange(plotlist=list(hosp_fig), nrow=1, legend="bottom",
           common.legend = FALSE)   
ggpubr::ggarrange(plotlist=list(icu_fig), nrow=1, legend="bottom",
           common.legend = FALSE)
ggpubr::ggarrange(plotlist=list(deaths_period), nrow=1, legend="bottom",
           common.legend = FALSE)   
ggpubr::ggarrange(plotlist=list(infections_period), nrow=1, legend="bottom",
           common.legend = FALSE)   
ggpubr::ggarrange(plotlist=list(icu_period), nrow=1, legend="bottom",
           common.legend = FALSE)
ggpubr::ggarrange(plotlist=list(hosp_period), nrow=1, legend="bottom",
           common.legend = FALSE) 
ggpubr::ggarrange(plotlist=list(vent_period), nrow=1, legend="bottom",
           common.legend = FALSE) 
ggpubr::ggarrange(plotlist=list(peak_vent), nrow=1, legend="bottom",
           common.legend = FALSE)                                
```

```{r plot_threshold1, fig.cap = cap, fig.height = 7}
# plot_event_time_by_geoid( 
#    hosp_county_peaks = thresholddat, 
#    shapefile = shp %>% mutate(name=as.character(name)), 
#    scenario_labels = config$report$formatting$scenario_labels[1], 
#    scenario_colors = config$report$formatting$scenario_colors[1], 
#    time_caption = paste("Time when", bedtype, "occupancy exceeds", bedtype, "bed capacity"), 
#    geoid_caption = "County",
#    value_name = "threshold_value", 
#    value_label = bedtype_label, 
#    start_date = config$start_date, 
#    end_date = config$end_date 
# )  
# cap <- paste("**Fig.", fig_counter, "** Time when COVID-19", bedtype, "occupancy exceeds in-county", bedtype, "bed capacity for", config$report$formatting$scenario_labels[1], "scenario at 1% IFR assumptions. We assume that occupancy is", occup_assum*100, "% over time for non-COVID patients. Points indicate the median and lines indicate the interquartile range of model estimates. Counties which never exceed capacity will have no estimate plotted.") 
# fig_counter <- fig_counter+1 
```



## Appendix 1: Methods

### Pipeline Overview

```{r, child=reference_chunk("PipelineDescription.Rmd")}
```

### Technical Details

#### Data Sources

* County-level confirmed SARS-COV-2 infections: [JHU CSSE COVID-19  Data Portal](https://coronavirus.jhu.edu/map.html)
  

* US Census Bureau 2010 county commuting flows and `r census_year` population data

Our model and report make the following key assumptions:

* Mean incubation period: `r incub_period` days

* Infectious period: ranges from `r paste(infect_period, collapse = "-")` days

* R0: `r paste(R0_range, collapse = "-")`

* We examine 3 infection fatality rates (IFR) throughout our report: `r paste0(config$hospitalization$parameters$p_death * 100, collapse = ", ")`%.

* We assume that `r paste0(config$hospitalization$parameters$p_death_rate * 100, "%")` of all hospitalized patients will die and adjust overall hospitalization rates to match the given IFR for a scenario.

* Hospitalizations admitted to the ICU: `r paste0(config$hospitalization$parameters$p_ICU*100, "%")`

* ICU admissions that are ventilated: `r paste0(config$hospitalization$parameters$p_vent*100, "%")`

<!-- * ICU occupancy is fixed at 68% over time for non-COVID-related patients for figures related to the time when bed occupancy exceeds capacity. ## UNCOMMENT IF BEDTYPE DATA IS AVAILABLE
 -->

#### Epidemic Simulation

[CHOOSE ONE OF THESE CHUNKS DEPENDING ON SEEDING. POISSON SEEDING TEXT SAYS 10X]
<!-- 
```{r, child=reference_chunk("importation_seeding.Rmd")}
```

```{r, child=reference_chunk("poisson_seeding.Rmd")}
``` -->

#### SEIR Model

```{r, child=reference_chunk("SEIRModelDesc.Rmd")}
```

### Limitations

```{r, child=reference_chunk("limitations.Rmd")}
```

### Key Sources

```{r, child=reference_chunk("key_sources.Rmd")}
```

## Development Team

[ADD NAMES AND RECOMPILE PACKAGE AS NECESSARY]
```{r, child=reference_chunk("DevelopmentTeam.Rmd")}
```

## Bibliography
